Analysis

### 2019-05-10 reports/DRM_exp/analysis_DRM_exp1.Rmd
new analysis
- new data from 9.5
- analysis for different payment types
- desctiptive analysis of participant sample

df <- readRDS(here::here("data/exp_DRM1/results_190425.rds"))

@@

if(!dir.exists(plots_dir)) {
  dir.create(plots_dir)
}
```

```{r filter participant which was not paying attention}
df <- df %>% filter(subject_id != 5)
```

@@

@@

df %>% 
  group_by(subject_id, type) %>% 
  summarize(correct = mean(correct)) %>% 
  ggplot(aes(x = type, y = correct)) +
  geom_point() +
  ylim(0,1) + theme(aspect.ratio = 1) +
  facet_grid(~subject_id)

@@

>>>>

df <- readRDS(here::here("data/exp_DRM1/results_190509.rds"))

df_participants <- readxl::read_excel(here::here("data/exp_DRM1/participants_190509.xlsx"))

@@

if(!dir.exists(plots_dir)) { dir.create(plots_dir) }

df <- df %>% left_join(df_participants, by = c("subject_id"))

@@

## Participant data

```{r participant desc}
df_participants %>% summarize(m_age = mean(age), sd_age = sd(age), n_males = sum(gender == "M"), n_payments = sum(payment == "yes")) %>% knitr::kable(digits=2)
```

@@

df %>% 
  group_by(subject_id, type) %>% 
  summarize(correct = mean(correct)) %>% 
  ggplot(aes(x = type, y = correct)) +
  geom_point() +
  ylim(0,1) + theme(aspect.ratio = 1) +
  facet_wrap(~subject_id)

@@

Analysis for first half and second half with respect to payment

df_acc2 %>% 
  group_by(type,part,payment) %>% 
  summarize(m = mean(correct), sd = sd(correct)) %>% 
  knitr::kable(digits = 2)

df_acc2 %>% 
  group_by(subject_id, type, part, payment) %>% 
  summarize(correct = mean(correct)) %>% 
  ggplot(aes(x = type, y = correct, col = part, group = part)) +
  stat_summary(fun.data = "mean_cl_boot") +
  stat_summary(fun.y = "mean", geom = "line") +
  ylim(0,1) + theme(aspect.ratio = 1) +
  facet_grid(~payment)

df_acc2 %>% 
  group_by(subject_id, payment) %>% 
  summarize(correct = mean(correct)) %>% 
  t.test(correct ~ payment, .)
```

The differences regarding payment is not significant.
